\documentclass[12pt,a4paper]{report}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage[
	backend=biber,
	style=authoryear,
	sorting=nyt,
	giveninits=true,
	maxbibnames=99,
	maxcitenames=2,
	date=year,
	doi=false,
	isbn=false,
	eprint=false,
	url=true
]{biblatex}

\addbibresource{references.bib}

\DefineBibliographyStrings{english}{
	urlseen = {Accessed}
}

\DeclareFieldFormat{urldate}{#1}

\hypersetup{
	colorlinks=true,
	linkcolor=black,
	citecolor=black,
	urlcolor=blue
}

\lstdefinelanguage{MatlabCode}{
	language=Matlab,
	morekeywords={function,end,ifft2,fft2,real,conj,sum,exp,abs,numel}
}

\lstset{
	language=MatlabCode,
	basicstyle=\ttfamily\small,
	keywordstyle=\bfseries,
	commentstyle=\itshape,
	columns=fullflexible,
	keepspaces=true,
	showstringspaces=false,
	frame=none
}

\setstretch{1.5}

\title{EPQ Title}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

\chapter{Introduction}

I chose this project because it connects well with subjects I already study, especially Physics and ICT. It lets me use what I have learnt in class in a more practical way, which makes the project more interesting and meaningful to me. I also like the idea of combining school knowledge with real life, rather than only learning theory.
Another reason is that I want to improve my Python skills. I have already learnt some programming, and this project gives me a good chance to practise writing code, solving problems, and working more independently. I think these are useful skills for both future study and everyday life.
I also chose this topic because tracking algorithms are already quite developed, so there are research papers and existing information I can look at. This makes it easier to understand the topic and compare different methods, while still giving me enough space to do my own investigation.


\chapter{Main Discussion}

Replace this text with your own content. Add each source to the bibliography file and cite it in the body of the report.

\begin{table}[htbp]
\centering
\caption{Matlab code, with a Gaussian kernel}
\label{tab:gaussian-kernel-code}
\begin{tabular}{@{}p{0.92\textwidth}@{}}
\toprule
\textbf{Inputs} \\
\quad $x$: training image patch, $m \times n \times c$ \\
\quad $y$: regression target, Gaussian-shaped, $m \times n$ \\
\quad $z$: test image patch, $m \times n \times c$ \\
[0.4em]
\textbf{Output} \\
\quad responses: detection score for each location, $m \times n$ \\
[0.6em]
\begin{minipage}{0.90\textwidth}
\begin{lstlisting}
function alphaf = train(x, y, sigma, lambda)
	k = kernel_correlation(x, x, sigma);
	alphaf = fft2(y) ./ (fft2(k) + lambda);
end

function responses = detect(alphaf, x, z, sigma)
	k = kernel_correlation(z, x, sigma);
	responses = real(ifft2(alphaf .* fft2(k)));
end

function k = kernel_correlation(x1, x2, sigma)
	c = ifft2(sum(conj(fft2(x1)) .* fft2(x2), 3));
	d = x1(:)' * x1(:) + x2(:)' * x2(:) - 2 * c;
	k = exp(-1 / sigma^2 * abs(d) / numel(d));
end
\end{lstlisting}
\end{minipage} \\
\bottomrule
\end{tabular}
\end{table}

\chapter{Conclusion}

The key requirement for AQA is consistency. This template gives you a clean and repeatable structure for in-text citations and the final reference list.

\printbibliography[title={References}]

\end{document}
